\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
Updates to theorems with HILL entropy

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon', s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

\subsection{Lossless Secure Sketch}
\label{sec:lossless sketch}
We now state a setting of parameters that yields a lossless sketch.  For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  There exist efficient lossless secure sketches based on \consref{cons:informal construction}:

@@

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.  A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.  Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.   \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) = H_\infty(W)$ for %the following parameters:
%\[
%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}

>>>>

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

\subsection{Lossless Secure Sketch}
\label{sec:lossless sketch}
We now state a setting of parameters that yields a lossless sketch.

@@

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe setting $q = poly(n)$.  
\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.  A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.  Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.   There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
%\[
%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
